MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-08-23 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

The advantages of community of Web services is that the community facilitates the discovery of web services and as community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via same standard protocols that a normal web services employs. But they requlate the service process via sophisticated internal communication protocols that result in providing a service out of combined work of a number of web services. The down side to communities is the management complexity that involves finding/inviting individual web services and managing the overall quality as combined work done by web services that although have similar functionality, but have different attitudes. Interacting with communities of web services, users send their requests to the coordinators of the community, which plays the role of the community representative or access point. The community coordinator in \emph{community centralized} architecture is responsible for task recieve/delivery issues. Moreover, as community representative, it verifies credentials of new web services before accepting them to join the community as well as firing web services, which do not add enough value to the community.

@@

>>>>

The advantages of community of Web services is that the community facilitates the discovery of web services and as community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via same standard protocols that a normal web services employs. But they requlate the service process via sophisticated internal communication protocols that result in providing a service out of combined work of a number of web services. The down side to communities is the management complexity that involves finding/inviting individual web services and managing the overall quality as combined work done by web services that although have similar functionality, but have different attitudes. Interacting with communities of web services, users send their requests to the coordinators of the community, which plays the role of the community representative or access point. The com munity coordinator in \emph{community centralized} architecture is responsible for task recieve/delivery issues. Moreover, as community representative, it verifies credentials of new web services before accepting them to join the community as well as firing web services, which do not add enough value to the community.

@@

Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $|n|$ web services. We define the following features for the group of web services based on their functional parameters:
